Lineage Analysis of CRISPR and shRNA Screens

### 2018-10-02 lineages_18Q3.Rmd

Load libraries.
```{r}
library(NMF)
library(ggpubr)
library(ggsignif)
library(rowr)
library(data.table)
library(CePa)
library(plyr)
library(tidyverse)
library(magrittr)
library(matrixStats)
library(parallel)
library(kableExtra)
library(gridExtra)
library(broom)
library(glmnet)
library(devtools)
library(reshape2)
library(caret)
library(bsselectR)
library(ComplexHeatmap)
library(circlize)
library(jsonlite)
```

@@

>>>>

Load libraries.
```{r}
library(NMF)
library(ggpubr)
library(ggsignif)
library(ggfortify)
library(ggord)
library(rowr)
library(data.table)
library(CePa)
library(plyr)
library(tidyverse)
library(magrittr)
library(matrixStats)
library(parallel)
library(kableExtra)
library(gridExtra)
library(broom)
library(glmnet)
library(devtools)
library(reshape2)
library(caret)
library(bsselectR)
library(ComplexHeatmap)
library(circlize)
library(jsonlite)
```

@@

```{r fig.height=12, fig.width=12}
crispr_pca_data <- merge(ccl_converter[, c("Broad_ID", "group_general_lineage_name")], crispr, by = "Broad_ID")
crispr_lin <- crispr_pca_data[, 2]
crispr_pca <- prcomp(data.matrix(crispr_pca_data[, 3:ncol(crispr_pca_data)]), scale. = TRUE, center = TRUE)
plot(crispr_pca, type = "l")
# autoplot(crispr_pca, data = crispr_pca_data, color = "group_general_lineage_name")
summary(crispr_pca)
biplot(crispr_pca, obs.scale = 1, var.scale = 1, groups = crispr_lin, ellipse = TRUE, circle = TRUE, )
ggord(crispr_pca, crispr_pca_data$group_general_lineage_name)
```
